\documentclass[12pt]{article}

\usepackage{pdflscape}
\usepackage[margin=0.8in]{geometry}
\usepackage{titling}
\usepackage{graphics} %Required for diagrams
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage{framed}
\usepackage{epsfig}
\usepackage{epstopdf}

\begin{document}

\input{coverPage.tex}

\newpage
\tableofcontents

\newpage
\listoffigures

\newpage

\section{Vision and scope}

\subsection{Project Background}
In the world of publishing; how books, magazines, graphic novels and other academic text are produced
predominantly using traditional means of publishing. There has not been much drive to leverage the
latest developments in technology.\\
The traditional manner of publishing allows limited room for collaboration and makes the production
life-cycle for a book long and tedious. The process of producing the book is still limited to the
editor and sub-editor working in collaboration, quality assurance remains the sole responsibility of the
publisher.\\
This has constrained the amount of books publishing houses produce over a set period of time. The
inability to seamlessly collaborate on text and quality assurance extends the production life cycle of a
book.
\subsection{Project vision}
Figbook aims to address the issue mentioned above. We intend to provide an application that will allow authors, agents, editors, copy-editors and designers to work on the book in an environment that encourages collaborative efforts and simplifies the life-cycle.\\
The system will allow multiple authors to collaboratively work on a project together so as to reduce the time spent on multi-authored works.\\
 
\subsection{Project scope}
The core of this project is to allow multiple authors to work on a book collayboratively. The system should allow smooth communication between different user roles at the different phases of the books life cycle.\\
The application will allow the authors to work on and see their project go from its infancy to the design and finally publishing phase.
\newpage
\section{Application requirements and design}
\par{This section discusses for each module of the Figbook system the functional requirements
as well as the process designs for the use cases and the domain models which must be maintained
within persistent storage by that module.
}

\input{authentication.tex}
\newpage

\input{manuscriptManagement.tex}
\newpage

\input{communication.tex}
\newpage


\end{document}
