\section{General Information}
\par{Figbook is an online collaborative writing system that facilitates writing/editing and styling a novel. It allows authors and editors to work on their project collaboratively in a central place.}

\section{System Overview}
\par{Figbook allows multiple authors to collaborate on a book online. It allows editors to log in and edit the manuscript and constantly communicate with authors about their project. \\ \\The system aims to provide a platform for different people in the publishing world (authors, editors, proof-readers etc) to come together and complete a project without having to constantly send manuscripts back and forth via email/mail etc.}

\section{System Configuration}
\par{Figbook is hosted online. Any users that wish to use it need an Internet connection and a web browser to access the website. Any operating system will run fine and the website is accessable from The following browsers: 
\begin{itemize}
\item Google Chrome
\item Mozilla FireFox
\item Internet Explorer
\item Safari
\end{itemize}

If your browser is not listed here, the site may work with limited functionality. }

\newpage
\section{User Access Levels}
In order to use the system users have to have an account. Simply open the URL and register an account. If there is any problems, please consult the tutorial on how to Register which is on the home page.

\section{Installing}
\par{In order to use this system, users must have a browser - with Javascript enabled - installed. If Javascript is not enabled on your browser then please consult the network administrator or computer administrator before you turn it on, as doing so does have some risks. \\ \\Enabling Javascript will allow websites to execute code on your browser to do certain tasks. Now while most websites use Javascript for functionality of their website, others may use it to perform malicious attacks on your computer. So if Javascript is not enabled, enquire with the PC owner/Administrator before turning it on. \\ \\If however you are the administrator and understand the risks of doing so, and wish to still enable it you can follow the screen shots in Appendix A at the back of the manual.}
