\textbf{Introduction}\paragraph{This section covers the different architectural factors that will place some constraints on the Figbook development. These constraints are divided into two categories as specified below. } 

\subsubsection{Technical Constraints}
\begin{itemize}
\item Programming languages - Figbook is a web-based application (fundamentally) and is being developed using the different html based languages mentioned in section 5(Technologies). The client however was requiring that there should be desktop and mobile interfaces, in which case the team will have to use programming languages outside the mentioned ones.These two additional interfaces will be made available only if time allows as they are nice to haves.

\item Operating systems supported - As Figbook is web based it should be on all OSs that support web browsers. The hosting of this application is provided in the Linux OS and is configurable to run on a Windows OS as well. 
\item Platforms supported -  These are the different browsers the application is required to run on.
\begin{itemize}
\item Internet Explorer -  Versions 9 to current.
\item Chrome -  Versions 42.* to current
\item Firefox -  Versions 87.* to current
\item Safari -  Versions 5.1 to current
\item Opera -  Versions 12.1* to current
\item iOS -  Versions 6.1 to current
\item Android -  Versions 2.3, 4.0 to current
\end{itemize}
\item Libraries and Frameworks - The client requested that we look into the Mediawiki library as it has collaborative writing in it. This meant that out of the different APIs available to build Figbook, mediawiki was a winner as suggested by the client.
\end{itemize}
\subsubsection{Business Constraints}
\begin{itemize}
\item Team composition - figbook is being developed by a group of 5, and the client provides advice on how we can complete the project, but all final decisions are made by and within the team.
\item Schedule - this project is to be completed within the dates specified by the University of Pretoria. The demo of the project will take place on the 23rd of October 2015, the project should be complete by that date.
\item Software licensing - all APIs and/or software used to deliver the Figbook application should be and is open source. This will make it possible for the project to be placed under the GPL V3 license after completion.
\end{itemize}



